\Title

### 2021-03-04 latex/paper/main.tex
Copied over acrobot's intertia, potential, etc to SecIV

%/========== Simulation ==========/%
\section{Simulation Results}\label{sec:simulations}

>>>>

TODO: after writing S2, re-introduce what we want to do with acrobot (energy
injection for giant stabilization)

For our model of the acrobot, we assume the acrobot iscomprised of two massless
rods of equal length \(l\), with equal point masses \(m\) at the tips.
We call this a \textit{simple} acrobot, which is displayed in Figure
\ref{fig:simple-acrobot-model}.
We will also ignore any frictional forces at both the hip and shoulder joints. 
Finally, it is important to note that a real gymnast cannot swing their legs in
full circles, though they are usually flexible enough to raise them parallel to
the floor; 
for this reason, we assume that \(q_a \in [-Q_a, Q_a]\) where 
\(Q_a \in [\frac{\pi}{2}, \pi[\).

\begin{figure}
    \centering
    %\includegraphics[width=0.5\textwidth]{images/simple_acrobot_model}
    \caption{A simple acrobot has massless rods of equal length \(l\) and 
    equal masses \(m\) at the tips.}
    \label{fig:simple-acrobot-model}
\end{figure}

This system has inertia matrix 
\(D\), potential function \(P\) (with respect to
the horizontal bar), and input matrix \(B\) given as follows:
\begin{align}\label{eqn:acrobot-inertia}
    D_s(q) &= \begin{bmatrix}
        ml^2\left(3+2\cos(q_a)\right) & 
        ml^2\left(1+\cos(q_a)\right) \\
        ml^2\left(1+\cos(q_a)\right) &
        ml^2
    \end{bmatrix} 
    , \\
    \label{eqn:acrobot-potential}
    P_s(q) &= -mgl\left(2\cos(q_u)+\cos(q_u+q_a)\right)
    , \\
    \label{eqn:acrobot-B}
    B &= [0;1]
    .
\end{align}
%/========== Simulation ==========/%
\section{Simulation Results}\label{sec:simulations}
